The Form of Uncertainty Affects Selection for Social Learning

### 2023-02-20 ms.tex
updates

%We found that the 
The evolution of social learning is a complex phenomenon, dependent on many interrelated factors, yet it is widespread across a
range of taxa. Although social learning is broadly studied, few studies have taken a systematic approach to understanding the role
of uncertainty in the evolution \edit{of} social learning. Understanding the role of uncertainty in social evolution is particularly important
for understanding human evolution as evidence increasingly suggests that the genus \emph{Homo} emerged in the context of substantial
(nonstationary) environmental variability \citep{anton_etal2014, levin2015}, and our global dispersal suggests that human groups regularly face novel environments. By carefully identifying and operationalizing different forms of uncertainty common in social-learning models, we developed a more thorough understanding of how uncertainty can favor social learning and how different forms of uncertainty interact to favor its evolution. By explicitly modeling a key individual-level learning mechanism shared across taxa, namely the ability to adjust behaviour to uncertainty and new information, we found that social learning could evolve even if it provides outdated information. %Social learning is a critical component of problem solving among social creatures. Our work identified and systematized some important forms of uncertainty and catalogued their effects on the evolution of social learning.
Our work, then, both advances the theory of social learning and could eventually be of practical use in identifying specific mechanisms underlying adaptations to an uncertain environments.

>>>>

%We found that the 
The evolution of social learning is a complex phenomenon, dependent on many interrelated factors, yet it is widespread across a
range of taxa. Although social learning is broadly studied, few studies have taken a systematic approach to understanding the role
of uncertainty in the evolution \edit{of} social learning. Understanding the role of uncertainty in social evolution is particularly important
for understanding human evolution as evidence increasingly suggests that the genus \emph{Homo} emerged in the context of substantial
(nonstationary) environmental variability \citep{anton_etal2014, levin2015}, and our global dispersal suggests that human groups regularly face novel environments. By carefully identifying and operationalizing different forms of uncertainty common in social-learning models, we developed a more thorough understanding of how uncertainty can favor social learning and how different forms of uncertainty interact to favor its evolution. By explicitly modeling a key individual-level learning mechanism shared across taxa, namely the ability to adjust behaviour to uncertainty and new information, we found that social learning could evolve even if it provides outdated information. %Social learning is a critical component of problem solving among social creatures. Our work identified and systematized some important forms of uncertainty and catalogued their effects on the evolution of social learning.
Our work, then, both advances the theory of social learning and could eventually be of practical use in identifying specific mechanisms underlying adaptations to uncertain environments.
